---
title: "Tidy_Noble"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(lubridate)

nobel_winners <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-14/nobel_winners.csv")
nobel_winner_all_pubs <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-14/nobel_winner_all_pubs.csv")



glimpse(nobel_winners)
nobel_winners %>% count(organization_name, sort=T)

```


#question: are nobel prize winners born in a certain month? or a certain day?


```{r}
nobel_winners %>% mutate(month_born =month(birth_date,label=T)) %>% count(month_born, sort = T)

nobel_winners %>% mutate(month_born =month(birth_date,label=T)) %>% ggplot(aes(month_born)) +
  geom_histogram(stat="count") 

#nice
nobel_winners %>% count(   month_born =month(birth_date,label=T)   ) %>%
  filter(!is.na(month_born)) %>% 
  ggplot(aes(month_born,n)) + geom_line(group=1, size=3, color="blue") + labs(x = "birth month",y = "", title= "Month that Nobel Prize Winners were born (1901-2016)", subtitle ="from TidyTuesday" ) 


nobel_winners %>% count(   month_die =month(death_date,label=T)   ) %>%
  filter(!is.na(month_die)) %>% 
  ggplot(aes(month_die,n)) + geom_line(group=1, size=3, color="blue") + labs(x = "month",y = "", title= "Month that Nobel Prize Winners died (1901-2016)", subtitle ="from TidyTuesday" ) 


#+ geom_text(aes(label = n), vjust = -4, hjust = 2, check_overlap = TRUE) 


nobel_winners %>% count(calendar_day = day(birth_date)) %>%
  filter(!is.na(calendar_day)) %>% 
  ggplot(aes(calendar_day,n)) + geom_line(group=1, size=3, color="blue") + labs(x = "birth month",y = "", title= "calendar  day that Nobel Prize Winners were born (1901-2016)", subtitle ="from TidyTuesday" ) 





nobel_winners %>% count(weekday_born = wday(birth_date, label=T))  %>% filter(!is.na(weekday_born)) %>%  ggplot(aes(x= weekday_born, y = n)) + geom_line(group=1, size=3, color="blue") + labs(x = "day",y = "", title= "day of the week that Nobel Prize Winners were born (1901-2016)", subtitle ="from TidyTuesday" ) 




```

<<<<<<< HEAD
but to be fair can see a simialr random pattern for death date?

UPDATED

#look at ages
how can we get age. might be over or under age by a year

```{r}
nobel_winners %>% mutate( age =  prize_year - year(birth_date)) %>% count(age, sort=T) %>% filter(!is.na(age)) %>%  ggplot(aes(age,n)) + geom_line(size=2, color="blue")


nobel_winners %>% mutate( age =  prize_year - year(birth_date)) %>% filter(age == 17)


nobel_winners %>% mutate( age =  prize_year - year(birth_date)) %>% group_by(gender) %>% filter(!is.na(gender)) %>% 
ggplot(aes(x=gender, y= age)) + geom_boxplot() + coord_flip()
```



#look at other set

```{r}
nobel_winner_all_pubs %>% count(category)
```

#does the lenht o the title tell us something abot nobel chance

```{r}
str_length()
nobel_winner_all_pubs %>% filter(laureate_id == 20001) %>% mutate(size = str_length(title))


nobel_winner_all_pubs  %>% mutate(size = str_length(title)) %>% View()

nobel_winner_all_pubs  %>% mutate(size = str_length(title)) %>% ggplot(aes( x = is_prize_winning_paper, y= size)) + geom_boxplot() + coord_flip() + labs(x = "did paper win prize", y = "", title = "length of a paper and if it won Nobel compared to other paper by winning authors")



nobel_winner_all_pubs  %>% mutate(size = str_length(title)) %>% ggplot(aes( x = is_prize_winning_paper, y= size, fill= is_prize_winning_paper )) + geom_boxplot() + coord_flip() + labs(x = "did paper win prize", y = "", title = "length of a winning paper  compared to other papers by winning authors") + facet_wrap(~category) + theme(legend.position = "none")

nobel_winner_all_pubs  %>% mutate(size = str_length(title)) %>% group_by(category) %>% summarise(mean(size, na.rm=TRUE))


nobel_winner_all_pubs  %>% mutate(size = str_length(title)) %>% group_by(category) %>% mutate(mean_length = mean(size, na.rm=TRUE)) %>% ggplot(aes(x=category, y= mean_length)) + geom_histogram(stat = "identity")

#how many pps do winning folks tend to write?

nobel_winner_all_pubs %>% group_by(laureate_id) %>% tally() %>% View()

 nobel_winner_all_pubs %>% group_by(laureate_id) %>% count(total_paper = count(title))


nobel_winner_all_pubs %>% filter(laureate_id == 20056) %>% View()

nobel_winner_all_pubs %>% group_by(laureate_id) %>% count(laureate_name)  %>% 
  ggplot(aes(y=laureate_name ,x=n)) + geom_boxplot()

```

